|

### 2021-09-24 03-Chp-Systematic-Review.Rmd
Back to a working version
End of day:

@@

Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist. These include randomised controlled trials, observational studies of different analytical design (cohort, case-control, etc), and Mendelian randomisation studies. However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types. Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association. As such, the primary aim of this analysis was to systematically review all available literature, regardless of study design.

Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence syntheists but may contain important unpublished studies. As an adjunct analysis to the systematic review presented in this chapter, I sought to quantify the additional evidential value of including preprints. This inclusion of preprint serves makes use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).

@@

In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes. Due to the scale of the project, this systematic review was performed in conjunction with a team of secondary reviewer. These included Alexandra MacAleenan, Athena Sheppard, Matthew Lee and Lena Schmidt. In addition, Sarah Dawson, and information specialist, provided input to the design of the search strategy.

@@

I systematically search electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records"). The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist. The strategy included terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed. An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy). <!-- TODO Need to actually attach each search strategy. Should be able to loop through search strategy results. -->

@@

The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection. As the contents of the Web of Science Core Collection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases). I also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.

In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies.

Grey literature was also searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. In addition, the abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. <!-- TODO how were these searched? Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"<!-- TODO CITATION NEEDED -->).

<!-- TODO Look at citationchaser for this, but have a cut-off publication date of July 2019 - better than searching by hand/Google Scholar -->

@@

Following deduplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.

@@

I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI. <!-- TODO Do I actually want to include MCI? --> Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.

Participants were free (or assumed to be free) of dementia/MCI <!-- TODO Do I actually want to include MCI? -->  at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression. No limits were placed on the sample size of included studies.

Eligible studies defined dementia according to recognised criteria, for example the International Classification of Diseases (ICD), National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. <!-- TODO CITATION NEEDED -->

__Bit on inclusion of EHR, where it is unclear how dementia diagnosed.__

@@

For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g. an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g. no dementia or dementia/MCI/dementia) based on this definition.

@@

Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews were excluded. Studies which present no evidence of attempting to exclude prevalent cases from their analyses were also excluded. Studies that measure change in continuous cognitive measures (e.g. MoCA score) without attempt to map these scores to ordinal groups (e.g. no dementia/MCI/dementia) were excluded. Conference abstracts with no corresponding full-text publication were examined, and I contacted authors to obtain information on the study's status. Studies that are reported in insufficient detail (e.g. only in conference abstracts, new, letters, editorials and opinion) were excluded. Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles. 
<!-- TODO Expand on rationale for exclusion of cross-sectional studies. Dementia is a disease severly at risk of differential recall, leading to misclassification bias. By using prospective studies, the potential for this bias is reduced. -->

Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g. for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) were excluded. Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet. Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.

@@

Inter- and intra-rater reliability during the screening stage were assessed for a 10% sub-sample of records at the title and abstract screening stage. Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e. assessment of conistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e. assessment of accuracy).

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does. [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is an important characteristic.

@@

How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement. Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

@@

If this assessment demonstrated issues with the screening process, a larger proportion of records would have been dual-screened.

@@

Data extraction was performed using a piloted data extraction form. Extracted items included: article metadata (year of publication, author list, journal), study characteristics (location, cohort name, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value). All data was extracted the data in the first instance and was checked for accuracy by a second member of the review team.

@@

Following best practice, where summary data was presented across two groups (e.g. age at baseline stratified by hypercholesterolemai status), the following approach was used to combine the groups <!-- TODO Cite cochrane handbook here -->

<!-- TODO Insert equations here -->

@@

This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script written to combine the groups for analysis. where more than one group

##

@@

Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorizing lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable. <!-- TODO This might not be as accurate now given the focus on dose response --> <!-- TODO Cross reference with the data extraction issues here - i.e. not providing qratile cut-off values, not poviding numbers per group, etc. --> Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:

@@

This was particularly relevant to preprints and published papers reporting the same study, which were not considered duplicate records. Instead, they were considered as different reports of the same study. This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.

@@

Where data points required either for the analysis or risk-of-bias assessment but were not reported, the primary authors of the study were contacted. This approach was taken due to the potentially large impact of following up with authors on the results of the review,[@reynders2019]

<!-- TODO Use the example of getting the cut-off points from the  -->

<!-- TODO move to results, and keep just a short bit here -->

@@

#### Converting between different exposure measures

@@

The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review. If the outcome is rare, odds and risk ratios approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account time-to-event in each treatment group.

Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect. In adddition, there is some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but this is not accurately documented in the review text.

<!-- TODO Need to really fix this -->

<!-- The likely effect of this is that the overall effect measures are biased towards . . . . ? -->

<!-- Can you predict the direction of effect from a  -->

<!-- Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis  -->

<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->

### Risk of bias assessment {#risk-of-bias}

A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Section \@ref(intro-triangulation) for the results of this qualitative analysis). To enable this triangulation exercise, a detailed and structured risk of bias assessment formed an important part of this review.

@@

This move was prompted by a unclear definition of "methodological quality" which could include facets such as, and challenges in the comparison of results from different tools. As part of this, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.

Additionally, results should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level. For example, a study may report on the efficacy of an intervention at 6 months and two years follow-up. missing outcome data that is not an issues at 6 months may introduce bias at 2 year follow-up. In this case, assigning a bias judgement to the study as a whole hides this differential biases for each result.

In this review, domain-based tools were used to assess the risk of bias for each result in each included study. The study design-specific tools are introduced and discussed in more detail in the following sections. In addition, the tool also aim to capture the potential direction of bias for each result. Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".

@@

Risk of bias assessment in randomised controlled trials was performed using the domain-based risk-of-bias assessment tool appropriate to the study design. Randomized controlled trials were assessed using the RoB2 tool.[@sterne2019]

The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result. Acceptable judgements include: low risk of bias, some concerns, high risk of bias. Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool. Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result. Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “Low risk”, “Moderate risk”, “Serious risk” and “Critical risk”. Ideally, observationals studies should be assessed in reference to an idealised randomised controlled trial. Further, the rare overall judgement of "Low" is considered equivalent to a randomised controlled trial.

For non-randomised studies of exposures (NRSE), I opted to use a preliminary version of the ROBINS-E tool.[@morganr2020] The tool is still in development, but while the signalling questions for each domain are yet to be confirmed, the overarching risk-of-bias domains have been finalised. The motivation for this using this tool above other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS. <!-- TODO CITATION NEEDED --> In addition, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs.

@@

At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies (advance results from this review were obtained from contact with the authors.). <!-- TODO CITATION NEEDED --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob).

@@

A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool. <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers. <!-- TODO CITATION NEEDED -->

This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence. This is because the tool did not exist when the protocol was originally registered.

@@

An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies across

Where individual studies were deemed comparable, they were incoroporated into a quantitative analysis or "meta-analysis". <!-- TODO CITATION NEEDED --> Meta-analysis provides a summary or pooled effect estimate across studies.

@@

<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.  -->

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results? --> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.

Where possible, data for all exposure groups was extracted. <!-- TODO ??? --> Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g. if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L).

<!-- Taken from another paper: "A potential non-linear association was evaluated using a restricted cubic spline model with three knots at the 10th, 50th and 90th percentile of frequency of the exposure [@orsini2012meta]" -->
<!-- TODO Do I initially want to fit a linear relationship across categories and  -->
A <!-- TODO confirm type of spline --> spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of an exposure can have an effect versus the "normal" reference dose. Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table). Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides. <!-- TODO Each bracket should have an upper and lower end -->

Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points. Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see \@ref(contacting-authors)).

When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the higest category was the same as the one immediately below it. Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).

@@

I conducted a leave-one-out analysis in order to explore the impact of any given study on the results. <!-- TODO CITATION NEEDED --> In addition, where available, I performed meta-regression to assess whether the results varied by age or sex.

<!-- TODO Need more here -->

@@

Further, given the importance of visualising the potential biases of a result alongside the result itself, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication).[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other reserachers to design a modular method for creating these plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using this tool.

>>>>

<!-- TODO text -->

@@

Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist. These include randomised controlled trials, observational studies of different analytical design, and Mendelian randomisation studies. However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types. Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association. As such, the primary aim of this analysis was to systematically review all available literature, regardless of study design.

Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but may contain important unpublished studies. As a sensitivity analysis to the systematic review presented in this chapter, I sought to quantify the additional evidential value of including preprints. This inclusion of preprint serves makes use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).

@@

In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes. Due to the scale of the project, this systematic review was performed in conjunction with a team of secondary reviewers and an information specialist (see Acknowledgments and Author declaration). <!-- TODO add the following to acknowledgements These included Alexandra MacAleenan, Athena Sheppard, and Matthew Lee.  In addition, Sarah Dawson, an information specialist, provided input to the design of the search strategy.-->

@@

I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records"). The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection. As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020a] the specific databases searched via this platform are listed in Appendix \@ref(appendix-wos-databases). The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist. The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed. An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy). <!-- TODO Need to actually attach each search strategy. Should be able to loop through search strategy results. -->

@@

I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials. In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies.

Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. In addition, the abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. <!-- TODO how were these searched? Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"<!-- TODO CITATION NEEDED -->).

@@

Following deduplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria. Additionally, records were rescreened by me with a 1 month lag to intra-rater consistency.

@@

I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia and its subtypes. Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.

Participants were screened for dementia at baseline and prevalent cases excluded. Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than <50 years of age at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression. No limits were placed on the sample size of included studies.

Eligible studies defined dementia according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that these criteria were used when entering the outcome into the EHR.

<!-- TODO Cite Peter Tennant's piece here on the problems with causal inference from analysis of change scores -->

@@

@@

Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though nested case-control studies, where historical records are used to determine the exposure status, were eligible for inclusion. Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded. Studies which presented no evidence of attempting to exclude prevalent cases from their analyses were also excluded. Studies that measure change in continuous cognitive measures (e.g. MoCA score) without attempt to map these scores to ordinal groups (e.g. no dementia/dementia) were excluded. Conference abstracts with no corresponding full-text publication were examined, and where required, I contacted authors to obtain information on the study's status. Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.

Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arms (e.g. for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) were excluded. Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet. Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.

@@

Inter- and intra-rater reliability during the screening stages were assessed for a 10% sub-sample of records. Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e. assessment of conistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e. assessment of accuracy).

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure was chosen over other methods such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does. [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is an important characteristic.

@@

How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement. Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrated issues with the screening process (defined as an AC1 of <.9), a larger proportion of records would have been dual-screened.

@@

Data extraction was performed using a piloted data extraction form. Extracted items included: article metadata (year of publication, author list, journal), study characteristics (study location, data source, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value). I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.

This was particularly relevant to preprints and published papers reporting the same study, which were not considered to be duplicate records but instead different reports of the same study. This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.

@@

Following best practice, where summary data was presented across two groups (e.g. age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups. [@higgins2019]

@@

This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script written to combine the groups for analysis.

@@

<!-- TODO This might not be as accurate now given the focus on dose response --> <!-- TODO Cross reference with the data extraction issues here - i.e. not providing qratile cut-off values, not poviding numbers per group, etc. --> Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:

@@

@@

Where additional data points not included in the report of an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted. This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]

@@

#### Analysis of varying effect measures

@@

The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review. If the outcome is rare, as is the case for dementia outcomes at and estimated prevalence of  odds and risk ratios approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-timea-at-risk in each treatment group. As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019]

Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect. In addition, there is some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but this is not accurately documented in the review text.
<!-- TODO Need to really fix this -->

In this review, studies reporting hazard ratios were synthesised separately to those reporting odds/risk ratios.

### Risk-of-bias assessment {#risk-of-bias}

A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Section \@ref(intro-triangulation) for the results of this qualitative analysis). To enable this triangulation exercise, a detailed and structured risk-of-bias assessment formed an important part of this review.

@@

This move was prompted by a unclear definition of "methodological quality" which could include facets such as unclear reporting, and challenges in the comparison of results from different tools. <!-- TODO CITATION NEEDED --> As part of this shift, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order. Additionally, bias should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level. For example, a study may report on the efficacy of an intervention at six months and two years follow-up. In this case, missing outcome data that is not an issue at six months may introduce bias at 2 year follow-up, and assigning a bias judgement to the study as a whole masks the different level of bias for each unique result.

In this review, domain-based tools were used to assess the risk of bias for each result in each included study. The study design-specific tools are introduced and discussed in more detail in the following sections.

@@

Randomized controlled trials were assessed using the RoB2 tool.[@sterne2019] The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result. Acceptable judgements include: low risk of bias, some concerns, high risk of bias. Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool. Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result. Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “Low risk”, “Moderate risk”, “Serious risk” and “Critical risk”. Ideally, observational studies should be assessed in reference to an idealised randomised controlled trial. Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to produced by a randomised controlled trial.

While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] but was insufficiently developed at the time the risk-of-bias assessments for this review were performed. Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (“Risk of Bias In Non-randomised Studies – of Exposure”), which I had applied in a published review.[@french2019] The version had no signalling questions and so judgements were made at the domain level. The motivation for this using this tool above other established tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS. Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs.

@@

At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the authors.). <!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy, and selection of participants.

@@

A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers. <!-- TODO Cite Ben's work on effect of missing study versus choice of analysis method -->

This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence. This is largely because the tool did not exist when the protocol was originally registered.

@@

An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design

Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis". <!-- TODO CITATION NEEDED --> Meta-analysis provides a summary or pooled effect estimate across studies.

@@

<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->

<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on. -->

<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks  -->

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results? --> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups. In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels.

Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not reported (e.g. if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands).

A restricted cubic spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of the exposure can have different effects versus a "normal" reference dose. The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data. Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table). Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.

Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points.

Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see Section \@ref(contacting-authors)).

When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the highest category was the same as the one immediately below it. Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).

@@

I conducted a leave-one-out analysis in order to explore the impact of any results on the summary effect estimate. <!-- TODO CITATION NEEDED --> In addition, where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics. _A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results. <!-- TODO Need more here -->

@@

One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.
